\emph{hp}-Finite Element Model of Poisson and Nernst-Planck System of Equations

### 2010-10-05 results.tex
Results sectioned better

\begin{figure}
  \begin{centering}
  \includegraphics[width=.8\columnwidth]{mesh}
  \caption{\label{fig:mesh} Initial coarse mesh (a),
  	half refined mesh (b) and refined mesh (c). The coarse mesh
	and refined mesh were used in the initial calcualtions, the latter one
	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
	used later to optimize \emph{hp}-adaptive mode solutions.}
  \end{centering}
\end{figure}
We ran the calculation for all the adaptivity types 
in both single-mesh and multi-mesh configurations. 
The following numeric results were recorded for each 
adaptivity type: converged error at each time step, cumulative CPU
time at each time step, and the problem size in terms of number
of degrees of freedoms (NDOFs) at each time step.  
Two types of initial meshes were used --- in case of only \emph{p}-adaptivity,
more refined mesh was used. When also the element size refinement
was enabled (all \emph{h} adaptivity types), very coarse initial mesh
was used. In any case, the initial mesh was loaded at each time step.

@@

Some initial observations
helped to select the graphs for this work --- it would have been unreasonable 
to present all recorded results for each adaptivity type.
First of all, the multi-mesh configuration resulted smaller problem size, faster
calculation, and better or similar error convergence than the single-mesh
configuration for all but HP\_ANISO\_H adaptivity type. In this case
the single-mesh configuration resulted slightly but not significantly
smaller problem size, therefore, single-mesh results of HP\_ANISO\_H
are considered in further comparisons. It must be also noted that in case of the isotropic
refinements, only P\_ISO adaptivity mode resulted in a reasonable problem size.
Secondly, H\_ISO did not converge very well in terms of the
calculation time and the problem size. The term ``reasonable problem size''
means that the number of degrees of freedom in time converges
to so that $N_{dof}<500$, and the term ``reasonable calculation time''
means that the calculation (step $\tau=0.01\ s$, physical
time $t_{end}=3.0\ s$) time $t$ on a givem system was $t<500\ s$.
Although these parameters are empirical, they serve as an upper limit, given
that the most adaptivity modes gave significantly smaller results,
e.g. $t<<500\ s$ and $N_{dof} << 500$.
Therefore, the multi-mesh calculation results H\_ISO, H\_ANSIO, P\_ANISO,
HP\_ANISO, HP\_ANISO\_P and the single-mesh calculation results of HP\_ANISO\_H
adaptivity mode will be compared. In all of the cases, the relative 
error at each time step remained below
the threshold which were set to $e_{th}=0.5\%$ between the coarse mesh
and fine mesh solutions.

>>>>

\begin{figure}
  \begin{centering}
  \includegraphics[width=.8\columnwidth]{mesh}
  \caption{\label{fig:mesh} Initial coarse mesh (a),
  	half refined mesh (b) and refined mesh (c). The coarse mesh
	and refined mesh were used in the initial calcualtions, the latter one
	in case of \emph{p}-adaptivity (including HP\_ANISO\_P). The half-refined mesh was
	used later to optimize \emph{hp}-adaptive mode solutions.}
  \end{centering}
\end{figure}
We ran the calculation for all the adaptivity types 
in both single-mesh and multi-mesh configurations. 
The following numeric results were recorded for each 
adaptivity type: converged error at each time step, cumulative CPU
time at each time step, and the problem size in terms of number
of degrees of freedoms (NDOFs) at each time step.  
Two types of initial meshes were used --- in case of only \emph{p}-adaptivity,
more refined mesh was used (see Fig.~\ref{fig:mesh}~(a)).
When also the element size refinement
was enabled (all \emph{h} adaptivity types), very coarse initial mesh
was used (see Fig.~\ref{fig:mesh}~(b)). 
In any case, the initial mesh was loaded at each time step.

@@

TODO COMpare ISO and ANiso meshes at some timesteps

\subsection{Adapted meshes and polynomial degrees}

Running the simulation with different adaptivity
types and meshes showed that the multi-mesh configuration generally results in
smaller problem size, faster calculation, and better or similar error convergence
compared to the single-mesh configuration. The only exception was HP\_ANISO\_H
adaptivity type for which the single mesh configuration resulted slightly
smaller problem size. It must be also noted that in case of the
isotropic refinements, only P\_ISO adaptivity mode resulted in a
reasonable problem size whereas H\_ISO and HP\_ISO did not converge
very well in terms of the calculation time and the problem size.
The term ``reasonable problem size''
means that the number of degrees of freedom in time converges
to so that $N_{dof}<500$, and the term ``reasonable calculation time''
means that the calculation (step $\tau=0.01\ s$, physical
time $t_{end}=3.0\ s$) time $t$ on a givem system was $t<500\ s$.
Although these parameters are empirical, they serve as an upper limit, given
that the most adaptivity modes gave significantly smaller results,
e.g. $t<<500\ s$ and $N_{dof} << 500$.
Some comparisons of problem sizes with a single-mesh configuration
vs. multi-mesh configurations are shown in: XXX

TODO SHOW SOME SAMPLE MESHES FOR DIFFERENT ADAPTIVITY TYPES

\subsection{Quantitative analysis of different adaptivity types}

Based on the results of the previous subsection, H\_ISO, H\_ANSIO, P\_ANISO,
HP\_ANISO, HP\_ANISO\_P and the single-mesh calculation results of HP\_ANISO\_H
adaptivity mode will be compared in terms of problem size and cumulative
CPU time. In all of the cases, the relative 
error at each time step remained below
the threshold which were set to $e_{th}=0.5\%$ between the coarse mesh
and fine mesh solutions, therefore the error vs. time plot is not considered.
